---
output:
  pdf_document: default
  html_document: default
---

```{r}
library(ggplot2)
```

Import Data
```{r}
# Import the dataset
nflx_df <- read.csv("C:/Users/benog/OneDrive/Documents/Grad School/USD/ADS 503 Predictive Modeling/Datasets/NFLX.csv")

# Add headers to the dataframe
#names(glass_df) <- c("Id_number", "RI", "Na", "Mg", "Al", "Si", "K", "Ca", "Ba", "Fe", "Type_of_glass")

head(nflx_df)
```

Find Null Values
```{r}
# Find number of null values for each attribute
missing_data <- colSums(is.na(nflx_df))
missing_data
```

Find Outliers
```{r}
# Use Tukey's method to find outliers
find_outliers <- function(x) {
  q <- quantile(x, probs=c(0.25, 0.75), na.rm=TRUE)
  iqr <- IQR(x, na.rm=TRUE)
  lower_bound <- q[1] - 1.5 * iqr
  upper_bound <- q[2] + 1.5 * iqr
  outliers <- x[x < lower_bound | x > upper_bound]
  return(outliers)
}

# Exclude the Date column
nflx_df_no_date <- nflx_df[, !names(nflx_df) %in% "Date"]

# Find the outliers for each predictor variable
outliers_list <- lapply(nflx_df_no_date, find_outliers)

# Display the outliers
names(outliers_list) <- names(nflx_df_no_date)
outliers_list
```

```{r}
# Use Tukey's method to find outliers and output to a dataframe
get_outliers_df <- function(x, dates) {
  q <- quantile(x, probs=c(0.25, 0.75), na.rm=TRUE)
  iqr <- IQR(x, na.rm=TRUE)
  lower_bound <- q[1] - 1.5 * iqr
  upper_bound <- q[2] + 1.5 * iqr
  outliers <- x[x < lower_bound | x > upper_bound]
  outlier_dates <- dates[x < lower_bound | x > upper_bound]
  return(data.frame(Value = outliers, Date = outlier_dates))
}

# Add the corresponding date to the outlier's value
outliers_list <- lapply(nflx_df_no_date, get_outliers_df, dates = nflx_df$Date)

# Combine outlier values and dates into a single dataframe
outliers_df <- do.call(rbind, outliers_list)
outliers_df
```

Create Box & Whisker Plots
```{r}
# Generate a distinct color for each variable
set_colors <- function(index) {
  colors <- c("lightgreen", "lightcoral", "lightpink", "lightyellow", "lightgrey", "lightblue")
  colors[(index %% length(colors)) + 1]
}

# Create boxplots for each variable in nflx_df except Date
boxplots <- lapply(seq_along(names(nflx_df)), function(i) {
  var <- names(nflx_df)[i]
  if (var != "Date") {
    ggplot(nflx_df, aes_string(x = "factor(1)", y = var)) +
      geom_boxplot(fill = set_colors(i), color = "black") +
      labs(x = "", y = var) +
      ggtitle(paste("Boxplot of", var))
  }
})

# Remove NULL values from the list
boxplots <- Filter(Negate(is.null), boxplots)

# Print each boxplot
for (plot in boxplots) {
  print(plot)
}
```

Create Histograms
```{r}
# Create histograms for each variable in nflx_df except Date
histograms <- lapply(seq_along(names(nflx_df)), function(i) {
  var <- names(nflx_df)[i]
  if (var != "Date") {
    ggplot(nflx_df, aes_string(x = var)) +
      geom_histogram(bins = 20, fill = set_colors(i), color = "black") +
      labs(x = var) +
      ggtitle(paste("Histogram of", var))
  }
})

# Remove NULL values from the list
histograms <- Filter(Negate(is.null), histograms)

# Print each histogram
for (plot in histograms) {
  print(plot)
}
```

Create Scatterplots
```{r}
# Generate a distinct color for each variable
set_color_scatter <- function(index) {
  colors <- c("skyblue", "lightcoral", "lightpink", "lightyellow", "lightgrey", "lightblue")
  colors[(index %% length(colors)) + 1]
}

# Create scatterplots for each variable in nflx_df showing the relationship with Adj. Close
scatterplots <- lapply(seq_along(names(nflx_df)), function(i) {
  var <- names(nflx_df)[i]
  if (var != "Adj.Close") {
    ggplot(nflx_df, aes_string(x = var, y = "Adj.Close")) +
      geom_point(color = set_color_scatter(i)) +
      labs(x = var, y = "Adj.Close") +
      ggtitle(paste("Scatterplot of", var, "vs. Adj. Close"))
  }
})

# Remove NULL values from the list
scatterplots <- Filter(Negate(is.null), scatterplots)

# Print each scatterplot
for (plot in scatterplots) {
  print(plot)
}
```

TODO: Not sure if using log transformations or any transformations is good for stock market data. This could lead to distorting true values and predictions since there are actual open, high, low, etc. numbers that represent an actual price or volume in time.
```{r}
# Create a copy of nflx_df
nflx_df_log <- nflx_df

# Exclude the "Date" and "Adj.Price" columns
cols_to_transform <- names(nflx_df_log)[!(names(nflx_df_log) %in% c("Date", "Adj.Price"))]

# Apply log transformation to numeric columns
for(col in cols_to_transform) {
  if(is.numeric(nflx_df_log[[col]])) {
    nflx_df_log[[col]] <- log(nflx_df_log[[col]])
  }
}

# Print the head of the transformed dataframe
print(head(nflx_df_log))

```

Create Histograms Using Normalized Data
```{r}
# Create histograms for each variable in nflx_df except Date
histograms <- lapply(seq_along(names(nflx_df_log)), function(i) {
  var <- names(nflx_df_log)[i]
  if (var != "Date" && var != "Adj.Close") {
    ggplot(nflx_df_log, aes_string(x = var)) +
      geom_histogram(bins = 20, fill = set_colors(i), color = "black") +
      labs(x = var) +
      ggtitle(paste("Histogram of", var))
  }
})

# Remove NULL values from the list
histograms <- Filter(Negate(is.null), histograms)

# Print each histogram
for (plot in histograms) {
  print(plot)
}
```














